### 2024-02-18 Chapter5.tex
Updated 2-layer after TV comments

\chapter[Application of models to HSI data]{Application of analytical tissue models to Hyperspectral Imaging data}\label{chap:HSImodel}
\begin{center}
\begin{minipage}[b]{0.9\linewidth}
\small
\textbf{Foreword\,}
This chapter is as yet unpublished. 
\newline
AB has conducted all of the research presented in this chapter under the supervision of JS, MB, and TV. The gelatin-based phantom images were kindly annotated by OM with the NHSI datasets being obtained via a collaborative study between KCL and HVS. 
\end{minipage}
\end{center}

@@

\subsection{Conclusion and Future Work}
In conclusion, this chapter shows that these models are able to obtain good quality results from quantitative snapshot hyperspectral data using well-defined optical properties, despite some oversimplification in the camera simulation. Relative data, however should be used with more caution demonstating a much larger impact of this camera simulation. When applied to neurosurgical hyperspectral linescan data, quantitative evaluation is more challenging due to the lack of known ground truth values. From visual inspection of this data, it appears that further work must be done to validate the modelling of the optical properties of these tissues. There is, however, promise that with an increased prior knowledge, these models may be able to provide valuable clinical parameters.

>>>>

\chapter[Application of models to HSI data]{Application of analytical tissue models to Hyperspectral Imaging data}\label{chap:HSImodel}
\begin{center}
\begin{minipage}[b]{0.9\linewidth}
\small
\textbf{Foreword\,}
This chapter is as yet unpublished. 
\newline
AB has conducted all of the research presented in this chapter under the supervision of JS, MB, and TV. The gelatin-based phantom images were annotated by OM. 
\end{minipage}
\end{center}

@@

\subsection{Conclusion and future work}
In conclusion, this chapter shows that these models are able to obtain good quality results from quantitative snapshot hyperspectral data using well-defined optical properties, despite some oversimplification in the camera simulation. Relative data, however should be used with more caution demonstating a much larger impact of this camera simulation. When applied to neurosurgical hyperspectral linescan data, quantitative evaluation is more challenging due to the lack of known ground truth values. From visual inspection of this data, it appears that further work must be done to validate the modelling of the optical properties of these tissues. There is, however, promise that with an increased prior knowledge, these models may be able to provide valuable clinical parameters.
